---
 title: "Homework One part 2"
 Author: "Melissa Pierre"
 date: "01/27/2020"
 output: "html_document"
---


## RMarkdown for Dataset exploration

**As the subtitle suggest, I will be analysing the mtcars data set by looking at the table, the structure and the summary.**

* MTcars data set was extracted from the 1974 Motor Trend US magazine. It includes the design, performance and fuel economy of 32 automobiles from 1973 - 1974.*

_Table of MTcars data below_

```{r, echo=FALSE}
mtcars
```
 **The table of the data set tells us the differents types of cars that were used.** 
 
_Sturcture of MTcars data below_

```{r, echo=FALSE}
str(mtcars)
```
**The structure of the data set tells us that 32 rows and 11 variables.**

_Names used in the structure below_

```{r, echo=FALSE}
names(mtcars)
```

_Mpg mean_

**The average mpg of all the cars is 20.1**
```{r, echo=FALSE}
mean(mtcars$mpg)
```


_Cyl mean_

**The average cyl of all the cars is 6.2** 
```{r, echo=FALSE}
mean(mtcars$cyl)
```

**To finish, we can see for each field the minimum, the 1st quadrant, the median, the mean,the 3rd Q, and the maximum)**
```{r, echo=FALSE}
summary(mtcars)
```


